General constraints on magic distillation protocols from statistical mechanics

### 2021-06-03 magic_paper.tex
Extension to relative majorization added. Details need adding+checking

In this direction, we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
\begin{equation}
D_\infty (\p ||\r) = \log \max_i \frac{p_i}{r_i}.
\end{equation}
This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states. In Appendix~\ref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
\begin{theorem} Let $\tau$ be in the interior of $\F$, and define the Wigner divergence $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$. Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
\begin{enumerate}
\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
\end{enumerate}
\end{theorem}
See Appendix~\ref{app:lcst_technical} for the proof of this. Moreover, in the appendices we also prove that for unital processes the Renyi entropies $H_{2m}(\w)$ are monotones for any $m \in \mathbb{N}$ and lead the generalized distillation bounds.
\begin{equation}
R \le \frac{H_{2m}(\rho)}{H_{2m}(\rho')}.
\end{equation}
It is of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.

@@

For an $\epsilon$-noisy Strange state, we have
\begin{equation}
	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
\end{equation}

We also have for any quantum state $\rho$ that
\begin{equation}
	H_{0}\left(\rho\right) = 2\log_2 3 = H_\alpha \left( \id/3 \right),
\end{equation}
for any $\alpha$, so the bound is not well-defined for $H_0$. \nick{this should be true for general relative majorization.}
\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}

>>>>

In this direction, we first note that the analysis for the temperature-dependent bound given by Equation (\ref{eq:rate_bounds_proof}) implicitly makes use of the single-shot Renyi divergence $D_\infty (\p ||\r)$, which is given by
\begin{equation}
D_\infty (\p ||\r) = \log \max_i \frac{p_i}{r_i}.
\end{equation}
This motivates defining the following \emph{Wigner divergence} $D_\infty(\rho, \tau) := D_\infty (W_\rho(\x) || W_\tau (\x))$ on all quantum states. In Appendix~\ref{app:lcst_technical}, we show that this divergence has the following natural properties that are derived via relative majorization.
\begin{theorem} Let $\tau$ be in the interior of $\F$, and define the Wigner divergence $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$. Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
\begin{enumerate}
\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
\end{enumerate}
\end{theorem}
See Appendix~\ref{app:lcst_technical} for the proof of this. Moreover, in the appendices we also prove that for unital processes the Renyi entropies $H_{2m}(\w)$ are monotones for any $m \in \mathbb{N}$ and lead the generalized distillation bounds.
\begin{equation}
R \le \frac{H_{2m}(\I/d)- H_{2m}(\rho)}{H_{2m}(\I/d)-H_{2m}(\rho')}.
\end{equation}
It is of interest to further explore this perspective and determine what components of single-shot information theory could be extended to quasi-distributions.

@@

For an $\epsilon$-noisy Strange state, we have
\begin{equation}
	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
\end{equation}
\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]}

We also have for any quantum state $\rho$ that
\begin{equation}
	H_{0}\left(\rho\right) = 2\log_2 3 = H_\alpha \left( \id/3 \right),
\end{equation}
for any $\alpha$, so the bound is not well-defined for $H_0$.

We extend to relative majorization via the following result.
\begin{lemma}Let $\w\in \mathbb{R}^N, \w'\in \mathbb{R}^{N'}$ be quasi-distributions and $\r\in \mathbb{R}^N, \r'\in \mathbb{R}^{N'}$ probability distributions with positive rational entries given by $r_i = a_i/K$ and $r_i' = a_i'/K$ for integers $a_i,K, a_i'$. Then
\begin{equation}
(\p, \r) \succ (\p', \r') \mbox{ if and only if } \Gamma_{\mathbf{a}} (\p) \succ \Gamma_{\mathbf{a}'} (\p'),
\end{equation}
and where $\Gamma_{\mathbf{a}} :\mathbb{R}^N \rightarrow \mathbb{R}^K$ is the map
\begin{equation}
\Gamma_{\mathbf{a}}(\x) := \bigoplus_{i=1}^N x_i \eta_{a_i},
\end{equation}
and $\eta_{a_i} = (1/a_i, 1/a_i, \dots, 1/a_i)$ is the uniform distribution on $a_i$ elements.
\end{lemma}
\begin{proof}
 The map $\Gamma_{\mathbf{a}}$ has a well-defined left-inverse $\Gamma^{-1}_{\mathbf{a}}: \mathbb{R}^K \rightarrow \mathbb{R}^N$ with 
\begin{equation}
\Gamma^{-1}_{\mathbf{a}}(\y) = ( \sum_{i=1}^{a_1} y_i,  \sum_{i=a_1 +1}^{a_1+a_2} y_i, \cdots ,  \sum_{i=a_1 +\cdots a_{N-1}+1}^{N} y_i),
\end{equation}
that obeys $\Gamma^{-1}_{\mathbf{a}} \circ \Gamma_{\mathbf{a}} (\x) = \x$ for all $\x \in \mathbb{R}^N$.

We now claim that a \emph{bistochastic map} $B$ exists that sends $\Gamma_{\mathbf{a}}(\w)$ to $\Gamma_{\mathbf{a}'}(\w')$ if and only if a stochastic map $A$ exists sending $\w$ to $\w'$ and $\r$ to $\r'$.

Suppose there is a stochastic map $A$ such that $A\w=\w'$ and $A\r = \r'$. We define $B := \Gamma_{\mathbf{a}'} \circ A \circ \Gamma_{\mathbf{a}}^{-1}$, and find that
\begin{align}
B \Gamma_{\mathbf{a}}(\w) &=\Gamma_{\mathbf{a}'} \circ A \circ \Gamma_{\mathbf{a}}^{-1}\circ\Gamma_{\mathbf{a}}(\w) \nonumber \\
&=\Gamma_{\mathbf{a}'} (\w').
\end{align}Moreover since $\Gamma_{\mathbf{a}} (\r) = (1/K, 1/K, \dots, 1/K)=\Gamma_{\mathbf{a}'} (\r') $ we also have that $B$ sends $(1/K, \dots ,1/K)$ to itself. \ddd{[To check that it also conserves probability and has non-negative components]}

Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\mathbf{a}}(\w)$ to $\Gamma_{\mathbf{a}'}(\w')$. Again, define  $A := \Gamma_{\mathbf{a}'}^{-1} \circ B \circ \Gamma_{\mathbf{a}}$, and find that $A$ is stochastic, and obeys $A\w = \w'$ and $A\r=\r'$. \ddd{[Spell out conditions for $A$ to be stochastic maybe]}.
\end{proof}
We also note that the vectors $\r, \r'$ with rational components is dense in the set of all positive probability distributions, and so we appeal to the fact that experiments have a finite resolution, and ignore technical details to do with the completion to arbitrary real components.

Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
This should provide relative majorization monotones from which we can obtain distillation bounds, such as
\begin{equation}
R \le \frac{H_\alpha(\tau) - H_\alpha (\rho)}{H_\alpha(\tau') - H_\alpha (\rho')}.
\end{equation}
\ddd{[To be checked]}
\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}
